---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
hrbrpkghelpr::global_opts()
```

```{r description, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::yank_title_and_description()
```

## NOTE

Minifying CSS and JavaScript requires another Rust module with some features enabled in `minify-html` that doesn't seem to work on arm64 Macs (yet). Ima figure it out and get that working at some point.

## What's Inside The Tin

The following functions are implemented:

```{r ingredients, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::describe_ingredients()
```

## Installation

```{r install-ex, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::install_block()
```

## Usage

```{r lib-ex}
library(minifyhtml)

# current version
packageVersion("minifyhtml")

```

```{r example}
'
<html xmlns="http://www.w3.org/1999/xhtml">
<head>
  <meta charset="UTF-8"/>
  <meta name="viewport" content="width=device-width, initial-scale=1"/>
  <!-- COMMENT -->
  <style>
    * { color: black; }
  </style>
  <title>TITTLE</title>
  </head>
  <body>
    <p>
       Some tex
    </p>
    <script>
      console.log("This is a console log message.");
    </script>
  </body>
</html>
' -> src

cat(minify(src))
```

```{r larger-example}
src <- httr::content(httr::GET("https://rud.is"), as = "text")

cat(substr(src, 1, 300))

cat(substr(minify(src), 1, 300))
```

## minifyhtml Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a Contributor Code of Conduct. 
By participating in this project you agree to abide by its terms.
